Inducing Semantic Frames on a Very Large Corpus of Syntactic-Ngrams

### 2015-01-03 Paper/paperN.tex
bit of rewriting

\section{Introduction}
The growing number of digital publications contains so much information that a single human being cannot process all this text, its even hard to keep up to date on a particular topic. It would be usefull to have technology that can create reliable summarizations. But not only quantity of information asks for such technology. For example for automatic stock trading systems, it would be usefull to know what is published about companies that are traded on the moment of publication.

The problem can be illustrated with a simple example: \textit{'Alice buys a bread from the baker'} descibes the exact same situation as \textit{`The baker sells Alice a bread'}. Thus the semantic content of these sentences can be represented in one frame, where the head of the frame represents the core of the episode or situation and involvement is expressed by assigning roles to things or people. In general these roles can be anything like location, time, manner etc. For the sentences above the frame is depicted in \ref{framex}.
\begin{wraptable}{r}{.3\textwidth}
  \centering
 % \begin{table}
\begin{tabular}{|l l|}
  \hline
  \textit{\small predicate:\normalsize}&Transaction\\
  \hline
  \hline
  \textit{\small role 1:\normalsize} &baker\\
  \textit{\small role 2:\normalsize} &Alice\\
  \textit{\small role 3:\normalsize} &bread\\
  \hline
\end{tabular}
%\end{table}
\caption{Simple frame}
\label{framex}
\end{wraptable}
The head of the frame, representing the core of the episode, can naturally be represented as a predicate but the trick is to find out which words have which roles. In linguistics this is called case grammar \citep{dowty1991} and roles have specific names as \textit{agent - patient}. In systems the names are not important and can be asigned when frame induction is complete.

As the example above shows, the roles are represented by different syntactic parts of speech in both sentences, the object and subject are switched, furthermore, the verbs are different. But even with knowledge of specific vebrs which bear the same meaning with switched subject/indirect-object, we need to have technology to let machines generate semantics next to syntacs in order to let machines be able to ( do as if they ) understand language and process new text in a meaningfull way. Hence, automatic semantic analysis and representation is required.

@@

In this project we investigate whether probabalistic latent-variable models can cluster verbs (as being a predicate) based on their meaning, which is inferred from the occurences of arguments it is encountered with. The clusters then make up the broader meaning of the predicates. The data we use contains triples of verb-subject-object (see section\ref{data}), so induced frames contain only two roles. The models (described in section \ref{models}) induce frames based on the assumption the meaning of a verb relative to meaning of other verbs can be induced from its context. Hence the broader meaning is latent. To evaluate our models we use two metrics, one of which uses framenet data, the other to check wheter the resulting frames are coherent. See section \ref{results} for more detail.

%\section{Related Work}
We based our work on two papers: \textit{`Inducing a semantically annotated lexicon via em-based clustering.'} by \citeauthor{rooth1999} and \textit{`Learning frames from text with an unsupervised latent variable model.'} by \citeauthor{oconnor2013}. In the first article clustering is realized by applying expectation maximalization on a simple model. This model produces frames in the form of 3 distributions, one for the predicate and two for the arguments. Frame assignement is result of calculating  probabilities for a given tuple, the frame that gives the highest probaility is then the assigned. We will use this model as our baseline (as in the O'Connor paper). The second paper covers multliple models of which we implemented one. The difference with the baseline model is the assumption that a document uses a set of frames repeatedly as a rsult of a document having a (couple of) topics. In our data the tuples are not annotated with documents so we used this assumption in such a way that each verb covers one document.

@@

\section{Experiments}
The number of frames in both models must be determined before induction. When choosing for a low number of frames the clusters will be bigger and thus the meaning of a cluster more vague. But a high number of frames has, next to high computational costs also a danger of overfitting the data. When unrelated verbs occur with the same arguments often they will be clustered and may even make up one cluster, while with a lower number of frames other verbs would be included, diminishing one of the unrelated verbs as noise.

The alphas and betas are known  to be hard to determine \citep{oconnor2013}, and therefore need experiments to be set to optimal values for a specific problem. We used, expensive but easy to implement, grid search to determine all parameters to test with. With grid-search a model is build with certain parameters, this model is then evaluated on a cross validation set. When all possible models are evaluated the highest scoring model is tested with a (kept aside) testset. We ran gridsearch for model 0 on 50 - 200 frames, with steps of 50, and $\alpha$ 0.1, 0.5, 1, 1.5, 2. Model 1 the same, and $\beta$ with values as $\alpha$

@@

\subsection{Frame Coherency}
The clusters of verbs are based on the arguments with which they are occuring in the data. So to test how well the models performed the probability of a triple in the testset, a real triple, should be greater than a triple with the verb replaced by a random one. This metric is the same as \citeauthor{rooth1999} used. More formally: for a datapoint $(v,s,o)$ and a tuple $(v^r,s,o)$ where $v^r$ is a random chosen verb: $P(v\mid s,o) \geq P(v^r\mid s,o)$.
The results are percentages of datapoints which satisfy this condition. Note though that if the random verb-triple is assigned the same frame as its `parent' real triple, this metric loses its meaning, but since the number of frames is high this probabilty is low. Furthermore, one can assume that the occurences of same frame assignement cancel eachother out, i.e. the random triple has higher probabilty than the real one as many times as vice versa.

>>>>

\section{Introduction}
The growing number of digital publications contains too much information for a single human being to process, it is even hard to keep up to date on a particular topic. It would be usefull to be aided by technology that creates reliable summarizations. To ceate a summary is to extract the semantic content of a text and represent it in a human readable output. The first part of such a technology, extract semantic content, could also be an advantage for automatic stock trading systems. If it knows what is published about companies that is traded on the moment of publication it can make more profit.

Semantic content of a sentence can be represented in a frame. The main verbphrase of the sentence is the head of the frame and can be interpreted as predicate, representing the core of the episode described by the sentence, but the trick is to find out what the arguments of the predicate are. In linguistics argument selection is called case grammar \citep{dowty1991} and arguments (or roles) have specific names as \textit{agent - patient}. In computational systems names are not important and can be asigned when frame induction is complete.
The problem of semantic content can be illustrated by this simple example: \textit{'Alice buys a bread from the baker'} descibes the exact same situation as \textit{`The baker sells Alice a bread'}. Thus the semantic content of these sentences can be represented in one frame, where the head of the frame represents the core of the episode or situation and involvement is expressed by assigning roles to things or people. In general these roles can be anything like location, time, manner etc. For the sentences above the frame is depicted in \ref{framex}.
\begin{wraptable}{r}{.3\textwidth}
  \centering
 % \begin{table}
\begin{tabular}{|l l|}
  \hline
  \textit{\small predicate:\normalsize}&Transaction\\
  \hline
  \hline
  \textit{\small role 1:\normalsize} &baker\\
  \textit{\small role 2:\normalsize} &Alice\\
  \textit{\small role 3:\normalsize} &bread\\
  \hline
\end{tabular}
%\end{table}
\caption{Simple frame}
\label{framex}
\end{wraptable}
As the example above shows, the roles are represented by different syntactic parts of speech in both sentences, the object and subject are switched, furthermore, the verbs are different. But even with knowledge of specific vebrs which bear the same meaning with switched subject/indirect-object, we need to have technology to let machines generate semantic representations on top of syntacs in order to let machines be able to ( do as if they ) understand language and process new text in a meaningfull way. Hence, automatic semantic analysis and representation is required for further automatization.

@@

In this project we investigate whether probabalistic latent-variable models can cluster verbs based on their meaning, which is inferred from the occurences of arguments it is encountered with. The clusters then make up a broader, but hopefully distinct, meaning. The data we use contains triples of verb-subject-object (see section \ref{data}), so induced frames contain only two roles. The models (described in section \ref{models}) induce frames based on the assumption the meaning of a verb relative to meaning of other verbs can be induced from its context. Hence the broader meaning is latent. To evaluate our models we use two metrics, one of which uses framenet data to check wheter the induced frames are similar to clusters of verbs in framenet, the other to check wheter the resulting frames are coherent, i.e. wheter the found clusters are not completely random. See section \ref{results} for more detail.

%\section{Related Work}
We based our work on two papers: \textit{`Inducing a semantically annotated lexicon via em-based clustering.'} by \citeauthor{rooth1999} and \textit{`Learning frames from text with an unsupervised latent variable model.'} by \citeauthor{oconnor2013}. In the first article clustering is realized by applying expectation maximalization on a simple model. This model produces frames in the form of 3 distributions, one for the predicate, a distribution over verbs, and two for the arguments, one distribution over subjects one over objects. A triple is assigned to a frame if the probability of this triple is highest in this frame. We will use this model as our baseline (as in the O'Connor paper). The second paper covers multliple models of which we implemented one. The difference with the baseline model is the assumption that a document uses a set of frames repeatedly as a rsult of a document having a (couple of) topics. [TODO: needs some further explanantion] In our data the tuples are not annotated with documents so we used this assumption in such a way that each verb covers one document.

@@

\section{Experiments}
The number of frames in both models mustar to be determined before induction can take place. When choosing for a low number of frames the clusters will be bigger and thus the meaning of a cluster more vague. In contrast, a high number of frames bears the danger of overfitting the data, i.e. when unrelated verbs occur with the same arguments often they will be clustered and may even make up one cluster, while with a lower number of frames other verbs would be included, diminishing one of the unrelated verbs as noise.

The alphas and betas are known  to be hard to determine \citep{oconnor2013}, and therefore need experiments to be set to optimal values for a specific problem. We used, expensive but easy to implement, grid search to determine all parameters to test with. Grid-search build for each posible parameter set a model which is evaluated on a cross validation set. The highest scoring model is tested with a (kept aside) testset. We ran gridsearch for model 0 on 50 - 200 frames, with steps of 50, and $\alpha$ 0.1, 0.5, 1, 1.5, 2. Model 1 the same, and $\beta$ with values as $\alpha$

@@

\subsection{Frame Coherency}
The clusters of verbs are based on the arguments with which they are occuring in the data. So to test how well the models performed on clustering, the probability of a triple in the testset, a real triple, should be greater than this triple with a random verb replacing the original one. This metric is the same as \citeauthor{rooth1999} used. More formally: for a datapoint $(v,s,o)$ and a tuple $(v^r,s,o)$ where $v^r$ is a random chosen verb: $P(v\mid s,o) \geq P(v^r\mid s,o)$.
The results are percentages of datapoints which satisfy this condition. Note though that if the random verb-triple is assigned the same frame as its `parent' real triple, this metric loses its meaning, but since the number of frames is high this probabilty is low. Furthermore, one can assume that the occurences of same frame assignement cancel eachother out, i.e. the random triple has higher probabilty than the real one as many times as vice versa.
